---
title: "RMD slides"
author: "Katrin Leinweber"
date: "2017-Mar-01"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## 2nd heading levels insert new slide

### Top-level heading

#### Sub-level heading

1. first
1. second (ordinal number doesn't matter)
1. third

a) Also produces 1.
a) B and 2.

***
Slide without a title

*italic*

**bold**

`for (i in len(x))`

## R consensus running code

`````{r, comment = "", echo = TRUE}
head(faithful)
```

`echo` argument controls display of code

`````{r, comment = "", echo = TRUE, eval = FALSE}
library(car)
head(Greene)
```

`eval` argument controls code execution & thus display of output

## Harry Plotter

```{r, echo=FALSE, fig.align='center', fig.cap="caption"}
plot(faithful$eruptions, faithful$waiting, 
     xlab = "eruptions", ylab = "waiting time")
```

***
Leaflet for maps, similar to `googlevis`

```{r, echo=TRUE, warning=FALSE}
library(leaflet)
my_map <- leaflet() %>%
  addTiles()

# %>% = pipe operator: equivalent to, but cleaner than:
# my_map <- leaflet()
# my_map <- addTiles(my_map)

my_map
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

